Temporal Activity Detection in Untrimmed Videos with RNN

### 2016-10-12 paper.tex
Start writing paper

\usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2016}

@@

\title{Formatting instructions for NIPS 2016}

@@

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch
  (3~picas) on both the left- and right-hand margins. Use 10~point
  type, with a vertical spacing (leading) of 11~points.  The word
  \textbf{Abstract} must be centered, bold, and in point size 12. Two
  line spaces precede the abstract. The abstract must be limited to
  one paragraph.
\end{abstract}

>>>>

%\usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{nips_2016}

@@

\title{Temporal Activity Detection in Untrimmed Videos with RNN}

@@

\author{
    Alberto Montes \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{al.montes.gomez@gmail.com} \\
    \And
    Amaia Salvador \\
    Image Processing Group \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{amaia.salvador@upc.edu} \\
    \And
    Xavi Giro-i-Nieto \\
    Image Processing Group \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{xavier.giro@upc.edu} \\
}

@@

\begin{abstract}
    In the later years the applications of Deep Learning techniques have moved from images to videos due to the increase of computational resources available. In this field and in the classification task 
\end{abstract}
